\documentclass[12pt, a4paper, titlepage]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{hyperref}


\author{Emma Marie Davenport}
\title{The Other Cemetery - Gameplay Doc}
\begin{document}

    \maketitle
    
    \section{Arcade Building}
    \subsection{Henry Saves The World}
    
    	\paragraph{Description} Similar to Galaga or Missile Command, the player will be represented as Henry. A horde of aliens is trying to land on earth, and it's your job to stop them. Using rockets and an assortment of weapons, you attempt to get a high score.
    
    	\paragraph{Gameplay} Enemies will appear from the top of the screen and move downwards semi randomly. Henry will be facing upwards. High scores will be persistent across loading
    and saving.
    
    \subsection{Henry Runs away from Aliens}
    
    	\paragraph{Description} Henry runs away from Aliens.
	
	\paragraph{Gameplay}  Henry will be running away from aliens that try to catch up to him. There will be obstacles in the way and it's your job to avoid them for as long as possible.
	
    \subsection{Henry Fights in Space}
    
    	\paragraph{Description} Henry uses a spaceship to destroy as many aliens as possible.
	
	\paragraph{Gameplay} Henry is represented as a simple triangle, while enemies are simple squares and circles. The triangle will be able to shoot at the squares and circles,
	causing them to explode in a ball of fire. If the player gets hit by a bullet or by an enemy colliding into them, they die.
	
	It would be interesting if there was a boost mechanic with the right mouse button. When the player presses it, they shoot faster and move faster for a short amount of time. The boost
	is displayed as a bar that depletes but eventually it recharges.
    
    \subsection{}
    
\end{document}