\documentclass[12pt, a4paper, titlepage]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{hyperref}


\author{Emma Marie Davenport}
\title{Disconnected Script}
\begin{document}

    \maketitle
    
    \section{Day Zero}

        \subsection{Funeral Home}

            ``Moving here was supposed to be a new change for my family. 
            However, I never anticipated that it would mean this \ldots\\~\\
	    I wanted to thank all of you for being here. Most of you
            don't know Duncan, but I am sure he would have appreciated it'' - Anna

        \subsection{Henry's Bedroom}

            ``Hey Bud, how are you doing?'' - Anna\\
            ``\ldots'' - Henry\\
            ``Yeah, me too. I miss them.'' - Anna says with some pause between each word spoken\\
            ``Well \ldots try to get some sleep tonight alright? You have to get back to school tomorrow'' - Anna\\
            ``Love you kiddo'' - Anna\\
            
	\section{Day One}

        \subsection{Henry's Bedroom}

            The player is now given control over Henry's movements. They are free to explore the tiny room and at some point
            they should make their way to the lobby of the home. Upon entering the lobby, he is greeted by his mother who is
            currently making some food in the kitchen.

            ``Hey, did you sleep well?'' - Anna\\
            ``\ldots'' - Henry\\
            ``Well either way, I made you some lunch. Don't forget to take it'' - Anna\\
            ``And try to have a good day today, okay? I know \ldots it's hard, but we'll get through this.'' - Anna

        \subsection{City}

            After the player has a conversation with their mother, they are free to leave home and explore the world. They are
            expected to go to school, however given the open world nature of this area, they might encounter some non-linear elements in the
            world.
            
            \paragraph{Grocer} they may explore the grocery store where they meet up with a character called Mr. Owen. Upon entering the building, the player
            will stumble upon a conversation between Mr. Owen and an unnamed woman. She'll leave, frustrated and Mr. Owen will mention that the player
            should be careful with the people in this this. That they, may end up killing him, although whether Mr. Owen was being true or not is a mystery.
            
            \paragraph{Collector} they may explore a building on the far left corner of main street. In this building, the woman will greet Henry as if
            nothing is wrong. However, if Henry attempts to go down a nearby staircase, the woman will tell Henry to get out and he'll be promptly kicked out. Forcing
            the player to try again. I think it would be interesting to have the player not have another attempt. So that different players may experience slightly different
            narratives.
            
            \paragraph{Church} will allow the player to visit a place that Henry is incredibly uncomfortable with. If he moves towards the end of the church, he'll be able
            to have a conversation with a church member. Their status or position in the church is unknown at this time.\\~\\
            
            ``Ahh Henry\ldots How are you feeling?'' - Member\\
            ``I\ldots I don't know why I'm here\ldots'' - Henry\\
            ``Well, there surely must be a reason'' - Member\\
            ``Everything, including losing a loved one, always has a reason'' - Member\\
            ``Don't you think Henry?'' - Member\\
            ``I\ldots suppose'' - Henry\\
            
            The camera will shift back to Henry, and the Member will be reciting the litany ``uo il atised'' if Henry is near him.
            
            \paragraph{Neighbour} the player will be able to enter the home of an npc. Upon entering the room the player will be able to listen in on a conversation between a woman and
            her husband.\\
            
            ``This time of year I can't stop thinking about Joy'' - Woman\\
            ``\ldots'' - Husband\\
            ``We should have just left'' - Woman\\
            ``You know we ca\ldots'' - Husband\\
            ``I miss her too.'' - Husband\\~\\

	\paragraph{Farthest Left Neighbour} the player is able to enter this home. Upon entering, a person will greet henry saying the following

	``Oh! Henry, you should have knocked'' - Person\\
	``Sorr\ldots'' - Henry\\
	``Oh, it's okay. It's not often you get to meet a\ldots'' - Person\\
	``I think it's been two years since the last one'' - Person\\
	``Hmm\ldots'' - Person\\
	``What do you mean?\ldots'' - Henry\\
	``Oh, nothing you have to worry about now'' - Person\\
            

            On this day, and this day alone, the city will be relatively busy. There will be people walking around, going into and out of buildings and school children
            playing and walking to school.

        \subsection{School}

            Upon entering the school, there will be no children in the halls. It'll seem empty at first glance. Henry will walk down the hallway and enter 
            his classroom which is literally at the end of the hall. He would have ran partially late, a school bell ringing just before he had even entered the building.
            
            As he enters the room, he will hear his teacher at the end of a conversation he was having with his students\\
            
            ``He is next\ldots'' - Teacher\\~\\
            The teacher will then notice henry and be somewhat startled.\\
            ``OH! Henry, why are you here today?'' - Teacher\\
            ``Shouldn't you be at home resting after what happened?'' - Teacher\\~\\
            Henry will have a thought\\
            ``He was talking about me\ldots''\\
            ``Well, take your seat Henry'' - Teacher\\
            Once Henry begins walking to his seat, a few text boxes will pop up. The screen fading to black.\\
            ``Our great founding fathers made a deal\ldots This deal has kept our town of willowstead safe for over a century.'' - Teacher\\~\\
            
            ``Now, who they made a deal with still remains a mystery, although we have our theories. It could be natives that had inhabited this region before, or maybe another force they had reckoned with\ldots'' - Teacher\\
            
            The screen will fade back in, no one in the classroom but henry. 
            
            The windows will be broken, tiles broken off from the ground. Henry will leave the room, into the school hallway. 
           
        \subsection{City}

	\paragraph{General}
        Until Henry goes home, the city will be relatively dead. This is no coincidence, but the player won't be none the wiser.
        
        Henry is able to explore the city and possibly enter a few new buildings in the city. If the player moves Henry to the top right corner of the map, you'll come across an area similar
        to that of Henry's dream. Except nothing will be there. Henry will however remark that this place seems oddly familiar. Henry may even remark that the city seems oddly dead. He 
        hasn't see it this way since before his brother died.
        
        If he enters any buildings, nobody will be around. However, certain buildings will be locked including the left building in main street and the home. The grocery store will be open, but 	Mr. 	Owen will be missing from his usual spot. Something Henry might remark as being a little odd.

	\paragraph{School Butchery}
	A woman, the one that notes that Henry and his mother are special, will come out from the left side of the school. This place has was previously locked but is now available. Inside this
	part of the school there will be three individuals talking in a semi-circle. You'll hear the tail end of their conversation.\\

	``It never feels right'' - Unknown\\
	``No, but we have to do it'' - Unknown2\\
	``At least it isn't one of your own, right?''  - Unkown2\\

	The men turn around, noticing henry.\\

	``Oh Henry\ldots'' - Unknown2\\
	``Shouldn't you be at home?'' - Unknown2\\
	``\ldots'' - Henry\\
	``Go Home Henry.'' - Unknown2\\

	Henry leaves

        \paragraph{Grocer}
        Outside of the Grocer, if the player originally went to check on Mr. Owen, the player will see two individuals talking.\\

	``Why do I have to go?'' - Girl\\
	``Everyone has to do their part'' - Guy\\
	``Now come on.'' - Guy\\        

        \subsection{Home}

            ``Hey! Did you have a good day at school?'' - Anna\\
            ``It\dots was okay.'' - Henry\\
            ``Well that's good to hear.'' - Anna\\
            ``I had a fairly weird day myself. I went to the grocery store to get some food and as I was going to checkout, I realized there wasn't anyone in the store'' - Anna\\
            ``I thought I had saw a clerk or two when I entered, but I don't know\ldots'' - Anna\\
            ``Anyways, I'm going to make dinner in an hour. So if you any homework or if you want to go play outside, now's your chance'' - Anna\\

            Henry will not want to do any homework. He's had a weird day, with that dream that had shaken him up. Instead, he decides he wants to go exploring. That's the only available 		   option presented to the player. This time, as he goes exploring he will see people outside of his house. Just looking at him, and when he approaches them they may walk away 		   and go into their house. They won't say anything to the player and henry will comment about how people are acting weird to him.
            
            As Henry goes exploring, he'll notice people out in the woods. Specifically in the area in the top right corner. They'll be saying something odd. ``We are ready. You will be 			   satisfied.'' However they will say it in a different tongue ``Ne rae eay. uo il atised''
            
            If you get closer to them, one of them will notice and approach you. Saying, ``We are ready for you''. It is at this point that the player will be placed into a chase sequence. If they 
            get away from their evader, Henry will go home. He won't see his mother, forcing him to yell ``MOM!''. She won't appear. Henry is already in the dead world. He will come to figure 	it out if he goes to his room, or if he goes outside once more.
            
            If you are unable to escape, then the player will be knocked out with a punch. The day will transition to the next day. He'll wake up, aware that he is in the dead world.
            
    \section{Day Two}
    
    	%\subsection{}
    
    \section{Day One - Anna's Perspective}
    
    	\subsection{After Dinner}
		
		``Where is this kid?'' - Anna, speaking to herself. Dinner having been finished 30 minutes prior, it's warm comfort quickly fading.
		Anna goes outside and screams ``Henry!'', ``Henry!? Dinner is ready!'', ``Where is he?''
		
		At this point the player will obtain control of Anna and will begin her search.

\end{document}